Automated verification of stand-alone solar photovoltaic systems

### 2018-11-13 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
updated bio
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{Lucas Cordeiro}
received his PhD degree from the University of Southampton in 2011. From 2009 to 2016, he was an Adjunct Professor at the UFAM (he is currently in unpaid leave). Since 2018, he is a Senior Lecturer at The University of Manchester, working with the Formal Methods Group.
\end{IEEEbiographynophoto}

>>>>

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{Lucas Cordeiro}
received his Ph.D. degree in Computer Science in 2011 from the University of Southampton, UK. Currently, he is a Senior Lecturer in the School of Computer Science at the University of Manchester, UK and leads the Systems and Software Verification laboratory. He is also a collaborator in the Postgraduate Program in Electrical Engineering and Informatics at the Federal University of Amazonas (UFAM), Brazil. Prior to joining the University of Manchester, he worked as a researcher / researcher engineer at Oxford University / Diffblue and as an adjunct professor at UFAM; he also worked for 4 years as a software engineer at Siemens Mobile and CT-PIM. His work focuses on software model checking, automated testing, program synthesis, and embedded \& cyber-physical systems.
\end{IEEEbiographynophoto}
